---
title: "Enhancement-dissemination"
output: pdf_document
date: "2024-01-17"
---

# Import data

```{r}
data = read.csv("/Users/huyanshen/Desktop/AI-Medicine/Research/Joyce/image-comparison/图像特征汇总-2024-Feb-13.csv")
# colnames(data)

#trim all the values with spaces
data[] <- lapply(data, function(x) if(is.character(x)) trimws(x) else x)

#delete redundant columns, and filter unnecessary molecular subtypes
data <- data[, !names(data) %in% c('手术时间', '年龄', '性别', '医院')]
data <- subset(data, `Molecular.Subtypes` %in% c('G3', 'G4', 'SHH', 'WNT'))

colnames(data)
data
```

```{r}
intrst_frame <- data[c("增强比例...Final", "Molecular.Subtypes")]
intrst_frame <- data[c("Molecular.Subtypes", "增强比例...Final")]
intrst_frame$"增强比例...Final" <- ifelse(intrst_frame$"增强比例...Final" == '10-90%', '50.0%', intrst_frame$"增强比例...Final")
intrst_frame <- intrst_frame[nchar(as.character(intrst_frame$增强比例...Final)) > 0, ]

intrst_frame <- intrst_frame[rowSums(sapply(intrst_frame, is.nan)) == 0, ]
intrst_frame[[name]] <- as.numeric(sub("%", "", intrst_frame[[name]])) / 100
Subtp <- intrst_frame[intrst_frame[["Molecular.Subtypes"]] == "SHH", ]
Subtp <- Subtp[["增强比例...Final"]]
#Subtp <- na.omit(Subtp)
median(Subtp)
```

# Enhancement pattern (4 groups)

## pattern #1

```{r}
library(DescTools)
#select the enhancement column and drop the empty string
interested_frame <- data[c("Molecular.Subtypes", "增强比例...Final")]
interested_frame <- interested_frame[nchar(as.character(interested_frame$增强比例...Final)) > 0, ]

#convert the percentage format into numeric format
interested_frame$增强比例...Final <- as.numeric(sub("%", "", interested_frame$增强比例...Final)) / 100

#divide the enhancement ratio column by the range of the ratio
breaks <- c(0, 0.3333, 0.6666, 1)
df_1 <- data.frame(subtype = interested_frame$Molecular.Subtypes, ratio = interested_frame$增强比例...Final)
df_1$ratio <- cut(interested_frame$增强比例...Final, breaks = breaks, labels = c("none/minimal (<10%)", "incomplete (1/3-2/3))", "diffuse (>=2/3)"), include.lowest = TRUE)

contingency_table <- table(df_1$ratio, df_1$subtype)
result_chi <- chisq.test(contingency_table, simulate.p.value = TRUE)
result_chi
result_G <- GTest(contingency_table)
result_G

total <- colSums(contingency_table)
contingency_table <- rbind(contingency_table, Total = total)

contingency_table <- contingency_table[, c(4, 3, 1, 2)]
write.csv(contingency_table, file = "./result.csv", row.names = TRUE)
df <- read.csv("./result.csv")
df
```

## pattern #2

```{r}
breaks <- c(0, 0.1, 0.5, 1)
df_1$ratio <- cut(interested_frame$增强比例...Final, breaks = breaks, labels = c("none/minimal (<10%)", "incomplete (10% - 50%))", "diffuse (>=50%)"), include.lowest = TRUE)

contingency_table <- table(df_1$ratio, df_1$subtype)
result_chi <- chisq.test(contingency_table[c(1, 2), ])
result_chi
rG <- GTest(contingency_table)
rG

total <- colSums(contingency_table)
contingency_table <- rbind(contingency_table, Total = total)

contingency_table <- contingency_table[, c(4, 3, 1, 2)]
write.csv(contingency_table, file = "./result.csv", row.names = TRUE)
df <- read.csv("./result.csv")
df
```

## pattern #3

```{r}

```

```{r}
#interested_frame$Molecular.Subtypes
WNT <- interested_frame[interested_frame$Molecular.Subtypes == "WNT", ]
WNT <- WNT$增强比例...Final


SHH <- interested_frame[interested_frame$Molecular.Subtypes == "SHH", ]
SHH <- SHH$增强比例...Final

G3 <- interested_frame[interested_frame$Molecular.Subtypes == "G3", ]
G3 <- G3$增强比例...Final

G4 <- interested_frame[interested_frame$Molecular.Subtypes == "G4", ]
G4 <- G4$增强比例...Final


result_anova <- aov(增强比例...Final ~ Molecular.Subtypes, data = interested_frame)
result_kruskal <- kruskal.test(增强比例...Final ~ Molecular.Subtypes, data = interested_frame)


summary(result_anova)
result_kruskal
#plot(result_anova)

print("median")
median(WNT)
median(SHH)
median(G3)
median(G4)

print("mean")
mean(WNT)
mean(SHH)
mean(G3)
mean(G4)
print("Q")

sd(WNT)
sd(SHH)
sd(G3)
sd(G4)
```

# Enhancement intensity(4 groups)

```{r}
interested_frame <- data[c("Molecular.Subtypes", "增强程度.相较于动静脉血管强化")]
interested_frame <- interested_frame[nchar(as.character(interested_frame$增强程度.相较于动静脉血管强化)) > 0, ]

contingency_table <- table(interested_frame$增强程度.相较于动静脉血管强化, interested_frame$Molecular.Subtypes)
result_chi <- chisq.test(contingency_table)
rG <- GTest(contingency_table)
rG

total <- colSums(contingency_table)
contingency_table <- rbind(contingency_table, Total = total)

contingency_table <- contingency_table[, c(4, 3, 1, 2)]
write.csv(contingency_table, file = "./result.csv", row.names = TRUE)
df <- read.csv("./result.csv")
df
result_chi
```

# Enhancement pattern(SHH)

```{r}
data = read.csv("./图像特征汇总-2024-1-18-shareYanshen.csv")
#colnames(data)

#trim all the values with spaces
data[] <- lapply(data, function(x) if(is.character(x)) trimws(x) else x)

#delete redundant columns, and filter unnecessary molecular subtypes
data <- data[, !names(data) %in% c('手术时间', '年龄', '性别', '医院')]
data <- subset(data, `Molecular.Subtypes` %in% c('SHH'))
data <- subset(data, `Genetic.Mutations` %in% c('TP53-', 'TP53+'))

colnames(data)
data
```

## pattern #1

```{r}
#select the enhancement column and drop the empty string
interested_frame <- data[c("Genetic.Mutations", "增强比例...Final")]
interested_frame <- interested_frame[nchar(as.character(interested_frame$增强比例...Final)) > 0, ]

#convert the percentage format into numeric format
interested_frame$增强比例...Final <- as.numeric(sub("%", "", interested_frame$增强比例...Final)) / 100

#divide the enhancement ratio column by the range of the ratio
breaks <- c(0, 0.3333, 0.6666, 1)
df_1 <- data.frame(subtype = interested_frame$Genetic.Mutations, ratio = interested_frame$增强比例...Final)
df_1$ratio <- cut(interested_frame$增强比例...Final, breaks = breaks, labels = c("none/minimal (<1/3)", "incomplete (1/3-2/3))", "diffuse (>=2/3)"), include.lowest = TRUE)

contingency_table <- table(df_1$ratio, df_1$subtype)
result_chi <- chisq.test(contingency_table, simulate.p.value = TRUE)
result_chi
result_G <- GTest(contingency_table)
result_G

total <- colSums(contingency_table)
contingency_table <- rbind(contingency_table, Total = total)

contingency_table <- contingency_table[, c(2, 1)]
write.csv(contingency_table, file = "./result0_1.csv", row.names = TRUE)
df <- read.csv("./result0_1.csv")

df$p.value <- ""
df$p.value[df$X == "none/minimal (<1/3)"] <- ifelse(result_chi$p.value < 0.001, "<0.001", sprintf("%.3f", result_chi$p.value))

write.csv(df, file = "./result0_1.csv", row.names = TRUE)
df
```

## pattern #2

```{r}
breaks <- c(0, 0.1, 0.5, 1)
df_1$ratio <- cut(interested_frame$增强比例...Final, breaks = breaks, labels = c("none/minimal (<10%)", "incomplete (10% - 90%))", "diffuse (>=90%)"), include.lowest = TRUE)

contingency_table <- table(df_1$ratio, df_1$subtype)

result_chi <- chisq.test(contingency_table[c(1, 2), ])
contingency_table[c(1,2), ]
result_chi
rG <- GTest(contingency_table[c(1, 2), ])
rG

total <- colSums(contingency_table)
contingency_table <- rbind(contingency_table, Total = total)

contingency_table <- contingency_table[, c(2, 1)]
write.csv(contingency_table, file = "./result0_2.csv", row.names = TRUE)
df <- read.csv("./result0_2.csv")

df$p.value <- ""
df$p.value[df$X == "none/minimal (<10%)"] <- ifelse(result_chi$p.value < 0.001, "<0.001", sprintf("%.3f", result_chi$p.value))

write.csv(df, file = "./result0_1.csv", row.names = TRUE)
df
```

## pattern #3

```{r}
TP53p <- interested_frame[interested_frame$Genetic.Mutations == "TP53+", ,]
TP53p <- TP53p$增强比例...Final

TP53m <- interested_frame[interested_frame$Genetic.Mutations == "TP53-", ]
TP53m <- TP53m$增强比例...Final

result_anova <- aov(增强比例...Final ~ Genetic.Mutations, data = interested_frame)
result_kruskal <- kruskal.test(增强比例...Final ~ Genetic.Mutations, data = interested_frame)
#tukey_result <- TukeyHSD(result_anova)


summary(result_anova)
result_kruskal

median(TP53p)
median(TP53m)

mean(TP53p)
mean(TP53m)

sd(TP53p)
sd(TP53m)
```

# Enhancement intensity

```{r}
interested_frame <- data[c("Genetic.Mutations", "增强程度.相较于动静脉血管强化")]
interested_frame <- interested_frame[nchar(as.character(interested_frame$增强程度.相较于动静脉血管强化)) > 0, ]

contingency_table <- table(interested_frame$增强程度.相较于动静脉血管强化, interested_frame$Genetic.Mutations)
result_chi <- chisq.test(contingency_table, simulate.p.value = TRUE)
rG <- GTest(contingency_table)

total <- colSums(contingency_table)
contingency_table <- rbind(contingency_table, Total = total)

contingency_table <- contingency_table[, c(2, 1)]
write.csv(contingency_table, file = "./result0_3.csv", row.names = TRUE)
df <- read.csv("./result0_3.csv")
df
result_chi
rG
```

# Dissemination(4 groups)

```{r}
data = read.csv("./CancerCell-2024-1-15-Dissemination-1.csv")
#colnames(data)

#trim all the values with spaces
data[] <- lapply(data, function(x) if(is.character(x)) trimws(x) else x)

#delete redundant columns, and filter unnecessary molecular subtypes
data <- data[, !names(data) %in% c('手术时间', '年龄', '性别', '医院')]
data <- subset(data, `Molecular.Subtypes` %in% c('G3', 'G4', 'SHH', 'WNT'))

colnames(data)
data
```

### Ependymal

```{r}
help("fisher.test")
```

```{r}
library(dplyr)

subtype <- c(rep("WNT", 0), rep("SHH", 3), rep("G3", 8), rep("G4", 14))
existence <- c(rep("y", 0), rep("n", 0),
            rep("y", 0), rep("n", 3),
            rep("y", 0), rep("n", 8),
            rep("y", 3), rep("n", 11))

test_frame <- data.frame(Subtype = subtype, Existence = existence)
test_table <- table(test_frame)
test_table <- t(test_table)
test_table <- test_table[, c(3, 1, 2)]
test_table
test_result <- fisher.test(test_table, simulate.p.value = TRUE)
test_result
```

```{r}
subtype <- c(rep("WNT", 105), rep("SHH", 200), rep("G3", 8), rep("G4", 14))
existence <- c(rep("y", 0), rep("n", 1),
            rep("y", 0), rep("n", 3),
            rep("y", 3), rep("n", 5),
            rep("y", 0), rep("n", 14))

test_frame <- data.frame(Subtype = subtype,Existence = existence)
test_table <- table(test_frame$Subtype, test_frame$Existence)
test_table <- t(test_table)
test_table <- test_table[, c(4, 3, 1, 2)]
y_table <- test_table[2, , drop=FALSE]
y_table
test_result <- chisq.test(y_table, 
                          simulate.p.value = TRUE
                          )
test_result
```

```{r}
ependaymal_data <- data[c("Molecular.Subtypes", "Ependymal.Dissemination")]
ependaymal_data <- ependaymal_data[nchar(as.character(ependaymal_data$Ependymal.Dissemination)) > 0, ]

totalTable <- table(ependaymal_data$Ependymal.Dissemination, ependaymal_data$Molecular.Subtypes)

totalTable <- totalTable[, c(4, 3, 1, 2)]
total <- colSums(totalTable)
totalTable <- rbind(totalTable, Total = total)
totalTable

ECmDp <- totalTable[2, , drop = FALSE]
ECpDp <- totalTable[1, , drop = FALSE]
ECpN <- totalTable[4, , drop = FALSE]
Etotal <- totalTable[5, , drop = FALSE]
```

```{r}
result1 <- chisq.test(ECmDp, simulate.p.value = TRUE)
ECmDp
result1

result2 <- chisq.test(ECpDp, simulate.p.value = TRUE)
ECpDp
result2

result3 <- chisq.test(ECpN, simulate.p.value = TRUE)
ECpN
result3

result4 <- chisq.test(Etotal, simulate.p.value = TRUE)
Etotal
result4
```

```{r}
data_c1 <- data.frame(
  Frequency1 = c(1, 3, 2, 5),  
  State1 = factor(c("State1", "State2", "State3", "State4"))
)
result1 <- kruskal.test(Frequency1 ~ State1, data = data_c1)



data_c2 <- data.frame(
  Frequency = c(0, 3, 0, 10),  
  State = factor(c("State1", "State2", "State3", "State4"))
)
result2 <- kruskal.test(Frequency ~ State, data = data_c2)


data_c3 <- data.frame(
  Frequency = c(0, 0, 0, 1),  
  State = factor(c("State1", "State2", "State3", "State4"))
)
result3 <- kruskal.test(Frequency ~ State, data = data_c3)


result1
result2
result3
```

### Ependymal+3rd V.I.R. Dissemination

```{r}
ependaymal_data <- data[c("Molecular.Subtypes", "Ependymal.3rd.V.I.R..Dissemination")]
ependaymal_data <- ependaymal_data[nchar(as.character(ependaymal_data$Ependymal.3rd.V.I.R..Dissemination)) > 0, ]

totalTable <- table(ependaymal_data$Ependymal.3rd.V.I.R..Dissemination, ependaymal_data$Molecular.Subtypes)

totalTable <- totalTable[, c(4, 3, 1, 2)]
total <- colSums(totalTable)
totalTable <- rbind(totalTable, Total = total)
totalTable

yes <- totalTable[3, , drop = FALSE]

r <- chisq.test(yes, simulate.p.value = TRUE)
yes
r
```

## 3.r.d VIR

```{r}
VIRdata <- data[c("Molecular.Subtypes", "X3rd.V.I.R..Dissemination")]
#VIRdata1 <- data[c("病人ID", "Molecular.Subtypes", "X3rd.V.I.R..Dissemination")]
#VIRdata1[VIRdata1$X3rd.V.I.R..Dissemination == "3. 3rd V.I.R. C-/D+", , ]
VIRdata <- VIRdata[nchar(as.character(VIRdata$X3rd.V.I.R..Disseminatio)) > 0, ]

totalTable <- table(VIRdata$X3rd.V.I.R..Disseminatio, VIRdata$Molecular.Subtypes)
totalTable <- totalTable[, c(4, 3, 1, 2)]
total <- colSums(totalTable)
totalTable <- rbind(totalTable, Total = total)
totalTable

VCmDp <- totalTable[3, , drop = FALSE]
VCpDp <- totalTable[1, , drop = FALSE]
VCpDm <- totalTable[2, , drop = FALSE]
VCpN <- totalTable[5, , drop = FALSE]
VTotal <- totalTable[6, , drop = FALSE]

r <- chisq.test(VCmDp, simulate.p.value = TRUE)
VCmDp
r

r <- chisq.test(VCpDp, simulate.p.value = TRUE)
VCpDp
r

r <- chisq.test(VCpDm, simulate.p.value = TRUE)
VCpDm
r

r <- chisq.test(VCpN, simulate.p.value = TRUE)
VCpN
r

r <- chisq.test(VTotal, simulate.p.value = TRUE)
VTotal
r
```

```{r}
# Creating the matrix
my_matrix <- matrix(c(1, 2, 3, 4), nrow = 1)

# Setting dimension names
dimnames(my_matrix) <- list("Row1" = c("Row1"), 
                            "Columns" = c("Column1", "Column2", "Column3", "Column4"))

# Converting to a table
my_table <- as.table(my_matrix)

# View the table
print(my_table)
```

## LMD

### sup LMD

```{r}
SupLMDdata <- data[c("Molecular.Subtypes", "Supratentorial.Leptomeningeal..LMD.")]
SupLMDdata <- SupLMDdata[nchar(as.character(SupLMDdata$Supratentorial.Leptomeningeal..LMD.)) > 0, ]

totalTable <- table(SupLMDdata$Supratentorial.Leptomeningeal..LMD., SupLMDdata$Molecular.Subtypes)
totalTable <- totalTable[, c(4, 3, 1, 2)]
total <- colSums(totalTable)
totalTable <- rbind(totalTable, Total = total)
totalTable

VCmDp <- totalTable[3, , drop = FALSE]
VCpDp <- totalTable[1, , drop = FALSE]
VCpDm <- totalTable[2, , drop = FALSE]
VCpN <- totalTable[4, , drop = FALSE]
VTotal <- totalTable[5, , drop = FALSE]

r <- chisq.test(VCmDp, simulate.p.value = TRUE)
VCmDp
r

r <- chisq.test(VCpDp, simulate.p.value = TRUE)
VCpDp
r

r <- chisq.test(VCpDm, simulate.p.value = TRUE)
VCpDm
r

r <- chisq.test(VCpN, simulate.p.value = TRUE)
VCpN
r

r <- chisq.test(VTotal, simulate.p.value = TRUE)
VTotal
r
```

### Inf LMD

```{r}
SupLMDdata <- data[c("Molecular.Subtypes", "Infratentorial.Leptomeningeal")]
SupLMDdata <- SupLMDdata[nchar(as.character(SupLMDdata$Infratentorial.Leptomeningeal)) > 0, ]

totalTable <- table(SupLMDdata$Infratentorial.Leptomeningeal, SupLMDdata$Molecular.Subtypes)
totalTable <- totalTable[, c(4, 3, 1, 2)]
total <- colSums(totalTable)
totalTable <- rbind(totalTable, Total = total)
totalTable

VCmDp <- totalTable[3, , drop = FALSE]
VCpDp <- totalTable[1, , drop = FALSE]
VCpDm <- totalTable[2, , drop = FALSE]
VCpN <- totalTable[4, , drop = FALSE]
VTotal <- totalTable[5, , drop = FALSE]

r <- chisq.test(VCmDp, simulate.p.value = TRUE)
VCmDp
r

r <- chisq.test(VCpDp, simulate.p.value = TRUE)
VCpDp
r

r <- chisq.test(VCpDm, simulate.p.value = TRUE)
VCpDm
r

r <- chisq.test(VCpN, simulate.p.value = TRUE)
VCpN
r

r <- chisq.test(VTotal, simulate.p.value = TRUE)
VTotal
r
```

### Sup + Inf

```{r}
SupLMDdata <- data[c("Molecular.Subtypes", "LMD.pattern")]
SupLMDdata <- SupLMDdata[nchar(as.character(SupLMDdata$LMD.pattern)) > 0, ]

totalTable <- table(SupLMDdata$LMD.pattern, SupLMDdata$Molecular.Subtypes)
totalTable <- totalTable[, c(4, 3, 1, 2)]
total <- colSums(totalTable)
totalTable <- rbind(totalTable, Total = total)
totalTable

VCmDp <- totalTable[1, , drop = FALSE]
VCpDp <- totalTable[3, , drop = FALSE]
VCpDm <- totalTable[2, , drop = FALSE]
VCpN <- totalTable[4, , drop = FALSE]
VTotal <- totalTable[5, , drop = FALSE]

r <- chisq.test(VCmDp, simulate.p.value = TRUE)
VCmDp
r

r <- chisq.test(VCpDp, simulate.p.value = TRUE)
VCpDp
r

r <- chisq.test(VCpDm, simulate.p.value = TRUE)
VCpDm
r

r <- chisq.test(VCpN, simulate.p.value = TRUE)
VCpN
r

r <- chisq.test(VTotal, simulate.p.value = TRUE)
VTotal
r
```

### All Dissemination

```{r}
ependaymal_data <- data[c("Molecular.Subtypes", "All.Dissemination")]
ependaymal_data <- ependaymal_data[nchar(as.character(ependaymal_data$All.Dissemination)) > 0, ]

totalTable <- table(ependaymal_data$All.Dissemination, ependaymal_data$Molecular.Subtypes)

totalTable <- totalTable[, c(4, 3, 1, 2)]
total <- colSums(totalTable)
totalTable <- rbind(totalTable, Total = total)
totalTable

yes <- totalTable[3, , drop = FALSE]

r <- chisq.test(yes, simulate.p.value = TRUE)
yes
r
```

## Dissemination (SHH)

```{r}
data = read.csv("./CancerCell-2024-1-15-Dissemination-1.csv")
#colnames(data)

#trim all the values with spaces
data[] <- lapply(data, function(x) if(is.character(x)) trimws(x) else x)

#delete redundant columns, and filter unnecessary molecular subtypes
data <- data[, !names(data) %in% c('手术时间', '年龄', '性别', '医院')]
data <- subset(data, `Molecular.Subtypes` %in% c('SHH'))
data <- subset(data, `Genetic.Mutations` %in% c('TP53-', 'TP53+'))

colnames(data)
data
```

### Ependymal

```{r}
ependaymal_data <- data[c("Genetic.Mutations", "Ependymal.Dissemination")]
ependaymal_data <- ependaymal_data[nchar(as.character(ependaymal_data$Ependymal.Dissemination)) > 0, ]

totalTable <- table(ependaymal_data$Ependymal.Dissemination, ependaymal_data$Genetic.Mutations)

totalTable <- totalTable[, c(2, 1)]
total <- colSums(totalTable)
totalTable <- rbind(totalTable, Total = total)
totalTable

ECmDp <- totalTable[2, , drop = FALSE]
ECpDp <- totalTable[1, , drop = FALSE]
#ECpN <- totalTable[4, , drop = FALSE]
Etotal <- totalTable[3, , drop = FALSE]

r <- chisq.test(ECmDp, simulate.p.value = TRUE)
ECmDp
r

r <- chisq.test(ECpDp, simulate.p.value = TRUE)
ECpDp
r

#result3 <- chisq.test(ECpN, simulate.p.value = TRUE)
#ECpN
#r

r <- chisq.test(Etotal, simulate.p.value = TRUE)
Etotal
r
```

### 3rd VIR

```{r}
ependaymal_data <- data[c("Genetic.Mutations", "X3rd.V.I.R..Dissemination")]
ependaymal_data <- ependaymal_data[nchar(as.character(ependaymal_data$X3rd.V.I.R..Dissemination)) > 0, ]

totalTable <- table(ependaymal_data$X3rd.V.I.R..Dissemination, ependaymal_data$Genetic.Mutations)

totalTable <- totalTable[, c(2, 1)]
total <- colSums(totalTable)
totalTable <- rbind(totalTable, Total = total)
totalTable

ECmDp <- totalTable[3, , drop = FALSE]
ECpDp <- totalTable[1, , drop = FALSE]
CpDm <- totalTable[2, , drop = FALSE]
ECpN <- totalTable[4, , drop = FALSE]
Etotal <- totalTable[5, , drop = FALSE]

r <- chisq.test(ECmDp, simulate.p.value = TRUE)
ECmDp
r

r <- chisq.test(ECpDp, simulate.p.value = TRUE)
ECpDp
r

r <- chisq.test(CpDm, simulate.p.value = TRUE)
CpDm
r

r <- chisq.test(ECpN, simulate.p.value = TRUE)
ECpN
r

r <- chisq.test(Etotal, simulate.p.value = TRUE)
Etotal
r
```

### Ependymal+3rd V.I.R. Dissemination

```{r}
ependaymal_data <- data[c("Genetic.Mutations", "Ependymal.3rd.V.I.R..Dissemination")]
ependaymal_data <- ependaymal_data[nchar(as.character(ependaymal_data$Ependymal.3rd.V.I.R..Dissemination)) > 0, ]

totalTable <- table(ependaymal_data$Ependymal.3rd.V.I.R..Dissemination, ependaymal_data$Genetic.Mutations)

totalTable <- totalTable[, c(2, 1)]
totalTable

EVtotal <- totalTable[3, , drop = FALSE]
r <- chisq.test(EVtotal, simulate.p.value = TRUE)
EVtotal
r

```

## LMD

### sup

```{r}
ependaymal_data <- data[c("Genetic.Mutations", "Supratentorial.Leptomeningeal..LMD.")]
ependaymal_data <- ependaymal_data[nchar(as.character(ependaymal_data$Supratentorial.Leptomeningeal..LMD.)) > 0, ]

totalTable <- table(ependaymal_data$Supratentorial.Leptomeningeal..LMD., ependaymal_data$Genetic.Mutations)

totalTable <- totalTable[, c(2, 1)]
total <- colSums(totalTable)
totalTable <- rbind(totalTable, Total = total)
totalTable

ECmDp <- totalTable[3, , drop = FALSE]
ECpDp <- totalTable[1, , drop = FALSE]
CpDm <- totalTable[2, , drop = FALSE]
ECpN <- totalTable[4, , drop = FALSE]
Etotal <- totalTable[5, , drop = FALSE]

r <- chisq.test(ECmDp, simulate.p.value = TRUE)
ECmDp
r

r <- chisq.test(ECpDp, simulate.p.value = TRUE)
ECpDp
r

r <- chisq.test(CpDm, simulate.p.value = TRUE)
CpDm
r

r <- chisq.test(ECpN, simulate.p.value = TRUE)
ECpN
r

r <- chisq.test(Etotal, simulate.p.value = TRUE)
Etotal
r
```

### Inf

```{r}
ependaymal_data <- data[c("Genetic.Mutations", "Infratentorial.Leptomeningeal")]
ependaymal_data <- ependaymal_data[nchar(as.character(ependaymal_data$Infratentorial.Leptomeningeal)) > 0, ]

totalTable <- table(ependaymal_data$Infratentorial.Leptomeningeal, ependaymal_data$Genetic.Mutations)

totalTable <- totalTable[, c(2, 1)]
total <- colSums(totalTable)
totalTable <- rbind(totalTable, Total = total)
totalTable

ECmDp <- totalTable[3, , drop = FALSE]
ECpDp <- totalTable[1, , drop = FALSE]
CpDm <- totalTable[2, , drop = FALSE]
ECpN <- totalTable[4, , drop = FALSE]
Etotal <- totalTable[5, , drop = FALSE]

r <- chisq.test(ECmDp, simulate.p.value = TRUE)
ECmDp
r

r <- chisq.test(ECpDp, simulate.p.value = TRUE)
ECpDp
r

r <- chisq.test(CpDm, simulate.p.value = TRUE)
CpDm
r

r <- chisq.test(ECpN, simulate.p.value = TRUE)
ECpN
r

r <- chisq.test(Etotal, simulate.p.value = TRUE)
Etotal
r
```

### sup + inf

```{r}
ependaymal_data <- data[c("Genetic.Mutations", "LMD.pattern")]
ependaymal_data <- ependaymal_data[nchar(as.character(ependaymal_data$LMD.pattern)) > 0, ]

totalTable <- table(ependaymal_data$LMD.pattern, ependaymal_data$Genetic.Mutations)

totalTable <- totalTable[, c(2, 1)]
total <- colSums(totalTable)
totalTable <- rbind(totalTable, Total = total)
totalTable

ECmDp <- totalTable[3, , drop = FALSE]
ECpDp <- totalTable[1, , drop = FALSE]
CpDm <- totalTable[2, , drop = FALSE]
ECpN <- totalTable[4, , drop = FALSE]
Etotal <- totalTable[5, , drop = FALSE]

r <- chisq.test(ECmDp, simulate.p.value = TRUE)
ECmDp
r

r <- chisq.test(ECpDp, simulate.p.value = TRUE)
ECpDp
r

r <- chisq.test(CpDm, simulate.p.value = TRUE)
CpDm
r

r <- chisq.test(ECpN, simulate.p.value = TRUE)
ECpN
r

r <- chisq.test(Etotal, simulate.p.value = TRUE)
Etotal
r
```

### All Dissemination

```{r}
ependaymal_data <- data[c("Genetic.Mutations", "All.Dissemination")]
ependaymal_data <- ependaymal_data[nchar(as.character(ependaymal_data$All.Dissemination)) > 0, ]

totalTable <- table(ependaymal_data$All.Dissemination, ependaymal_data$Genetic.Mutations)

totalTable <- totalTable[, c(2, 1)]
totalTable

EVtotal <- totalTable[3, , drop = FALSE]
r <- chisq.test(EVtotal, simulate.p.value = TRUE)
EVtotal
r
```

## New method

```{r}
table_fisher <- matrix(c(4,101,
                         40,160,
                         17,67,
                         57,242), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,1,3,3,0,2,10,11), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(1,0,3,3,2,0,5,15), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(1,3,6,34,2,15,21,36), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,2,1,8,0,6,4,16), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(1,0,4,4, 4, 2, 10, 8), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,1,3,5,2,4,1,17), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(2,2,9,31,6,11,20,37), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(2,2,13,27,6,11,31,26), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,1,1,12,0,3,0,12), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(1,0,5,6,1,1,5,3), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,1,5,6,1,1,3,5), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(1,3,13,27,3,14,12,45), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,1,1,20,0,13,0,18), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,0,12,4,8,3,12,1), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,0,3,13,3,8,1,12), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(1,3,
                         21,19,
                         13,4,
                         18,39), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,2,
                         2,29,
                         0,13,
                         0,29), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(1,0,
                         16,8,
                         8,3,
                         17,4), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,1,
                         6,18,
                         3,8,
                         4,17), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(2,2,
                         31,9,
                         13,4,
                         29,28), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(1,2,
                         2,1), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(2,1,
                         1,2), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(3,8,
                         3,22), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(1,1,
                         0,7), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,2,
                         4,2), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(1,1,
                         2,4), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(2,9,
                         7,18), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(5,6,
                         8,17), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,6,
                         1,6), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(2,2,
                         3,4), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(6,5,
                         7,18), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,4,
                         1,8), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(3,1,
                         7,2), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(1,3,
                         1,8), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(4,7,
                         13,12), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(0,8,
                         2,17), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(4,2,
                         10,5), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(2,4,
                         3,12), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(8,3,
                         19,6), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```

```{r}
table_fisher <- matrix(c(11,44,
                         25,103), nrow = 2)
table_fisher
result_fisher <- fisher.test(table_fisher)
print(result_fisher)
```
