---
title: "R Notebook"
output: html_notebook
---

First, to create a data frame in R, you can do as straightforward as this:

```{r}
my_array <- array(1:18, dim = c(2, 9))
my_df <- as.data.frame(my_array)
colnames(my_df) <- c("Column1", "Column2", "Column3",
                     "Column4", "Column5", "Column6",
                     "Column7", "Column8", "Column9")
lst <- c("Column1", "Column2", "Column3")
rownames(my_df) <- c("Row1", "Row2")
#my_df[,1] <-paste(as.character(my_df[,1]), "(",sprintf("%.2f%%", my_df[,1]), ")")  
my_df
my_df[1, "Column9"]
```

```{r}
library(DescTools)
calc_p <- function(name, subtype, dataframe) {
  intrst_frame <- dataframe[c(name, subtype)]
  intrst_frame <- intrst_frame[nchar(as.character(intrst_frame[[name]])) > 0, ]
  intrst_frame[[name]] <- ifelse(intrst_frame[[name]] == '1. Y', "Y", intrst_frame[[name]])
  intrst_frame[[name]] <- ifelse(intrst_frame[[name]] == '2. N', "N", intrst_frame[[name]])

  if('Y' %in% intrst_frame[[name]]){
    intrst_frame <- intrst_frame[intrst_frame[[name]] %in% c("Y", "N"), ]
  }
  contigtab <- table(intrst_frame)
  chi_p <- chisq.test(contigtab, simulate.p.value = TRUE)$p.value
  try_fisher <- try(fisher.test(contigtab, simulate.p.value = TRUE), silent = TRUE)
  fisher_p <- ifelse(class(try_fisher)=='try-error', -1, fisher.test(contigtab, simulate.p.value = TRUE)$p.value)
  G_p <- GTest(contigtab, correct = "williams")$p.value
  return(c(chi_p, fisher_p, G_p))
}

```

``` r

1/2
```

```{r}
#import the data frame
data <- read.csv('/Users/huyanshen/Desktop/untitled folder/图像特征汇总-2024-Feb-13.csv')

#trim all the values with spaces
data[] <- lapply(data, function(x) if(is.character(x)) trimws(x) else x)

filtered_data <- subset(data, `Molecular.Subtypes` %in% c('G3', 'G4', 'SHH', 'WNT'))


#pick out the columns to be dealt with
col_list <- c("Fourth.ventricle.Infiltration", "肿瘤边界..Tumor.Margin.", "水肿", "囊肿.坏死.cyst.cavitation.change", "脑积水.手术前.", "脑部.M2.转移")

#organize the first table
tumor_location <- filtered_data[c("肿瘤位置", "Molecular.Subtypes")]
tumor_location <- tumor_location[nchar(as.character(tumor_location$"肿瘤位置")) > 0, ]
contigtab <- table(tumor_location)
contigtab <- contigtab[,c(4, 3, 1, 2)]
total <- colSums(contigtab)
contigtab <- rbind(contigtab, Total = total)

#write the first csv1
write.csv(contigtab, file = "./result.csv", row.names = TRUE)

#change the cell format into A1(B2%)
df <- read.csv("./result.csv", row.names = 1)
df0 = df
for (i in 1:nrow(df)) {
  df0[i, ] <- df[i,]/df[nrow(df),] 
}
for (l in 1:nrow(df)) {
    df[l, ] <- paste(as.character(df[l, ]), "(", sprintf("%.2f%%", df0[l, ] * 100), ")")
}

#rewrite the csv1
write.csv(df, file="./result.csv")
df <- read.csv("./result.csv")
df <- cbind(NewColumn = rep("", nrow(df)), df)
df[1, 1] <- "Six classes"
df <- cbind(df, "p-value(chi-square)" = rep("", nrow(df)), 
            "p-value(Fisher exact)" = rep("", nrow(df)), 
            "p-value(G-test)" = rep("", nrow(df)) )

result_p <- calc_p("肿瘤位置", "Molecular.Subtypes", filtered_data)

df[1, "p-value(chi-square)"] <- ifelse(result_p[1] >= 0.001, sprintf("%.3f", result_p[1]), "<0.001")
if (result_p[2] == -1) {
  df[1, "p-value(Fisher exact)"] = -1
}else{
  df[1, "p-value(Fisher exact)"] <- ifelse(result_p[2] >= 0.001, sprintf("%.3f", result_p[2]), "<0.001")
}
df[1, "p-value(G-test)"] <- ifelse(result_p[3] >= 0.001, sprintf("%.3f", result_p[1]), "<0.001")
write.csv(df, file="./result.csv", row.names = FALSE)

#for loop
for (name in col_list) {
  intrst_frame <- filtered_data[c(name, "Molecular.Subtypes")]
  intrst_frame <- intrst_frame[nchar(as.character(intrst_frame[[name]])) > 0, ]
  intrst_frame[[name]] <- ifelse(intrst_frame[[name]] == '1. Y', "Y", intrst_frame[[name]])
  intrst_frame[[name]] <- ifelse(intrst_frame[[name]] == '2. N', "N", intrst_frame[[name]])

  if('Y' %in% intrst_frame[[name]]){
    intrst_frame <- intrst_frame[intrst_frame[[name]] %in% c("Y", "N"), ]
  }
  # organize the table
  contigtab <- table(intrst_frame)

  contigtab <- contigtab[, c(4, 3, 1, 2)]
  if('Y' %in% intrst_frame[[name]]) {
    contigtab <- contigtab[c(2, 1),]
  }
  total <- colSums(contigtab)
  contigtab <- rbind(contigtab, Total = total)
  #write the table into csv2
  write.csv(contigtab, "./tempt.csv", row.names = TRUE)
  #read and change the cell format into A1(B2%)
  df <- read.csv('./tempt.csv', row.names = 1)
  df0 = df
  for (j in 1:nrow(df)) {
    df0[j, ] <- df[j,]/df[nrow(df),] 
  }
  for (k in 1:nrow(df)) {
    df[k, ] <- paste(as.character(df[k, ]), "(", sprintf("%.2f%%", df0[k, ] * 100), ")")
  }
  
  write.csv(df, file="./tempt.csv")
  df <- read.csv("./tempt.csv")
  df <- cbind(NewColumn = rep("", nrow(df)), df)
  df[1, 1] <- name
  
  df <- cbind(df, "p-value(chi-square)" = rep("", nrow(df)), 
            "p-value(Fisher exact)" = rep("", nrow(df)), 
            "p-value(G-test)" = rep("", nrow(df)) )

  result_p <- calc_p(name, "Molecular.Subtypes", filtered_data)

  df[1, "p-value(chi-square)"] <- ifelse(result_p[1] >= 0.001, sprintf("%.3f", result_p[1]), "<0.001")
  if (result_p[2] == -1) {
    df[1, "p-value(Fisher exact)"] = -1
  }else{
    df[1, "p-value(Fisher exact)"] <- ifelse(result_p[2] >= 0.001, sprintf("%.3f", result_p[2]), "<0.001")
  }
  df[1, "p-value(G-test)"] <- ifelse(result_p[3] >= 0.001, sprintf("%.3f", result_p[1]), "<0.001")
  
  # Append csv2 to csv1 without column names
  write.table(df, file = "./result.csv", append = TRUE, col.names = FALSE, row.names = FALSE, sep = ",", quote = TRUE)
  
} 

```

```{r}
help("read.csv")
```

# Imaging features-分子亚型

## Data frame with missing values dropped

```{r}
data <- read.csv('/Users/huyanshen/Desktop/untitled folder/图像特征汇总-2024-Feb-13.csv',)

#trim all the values with spaces
data[] <- lapply(data, function(x) if(is.character(x)) trimws(x) else x)

print(colnames(data))
data
```

## Data filtered by Molecular Subtype

```{r}
filtered_data <- subset(data, `Molecular.Subtypes` %in% c('G3', 'G4', 'SHH', 'WNT'))
```

### Tumor location with six classes

```{r}
tumor_location <- filtered_data[c("肿瘤位置", "Molecular.Subtypes")]
tumor_location <- tumor_location[nchar(as.character(tumor_location$"肿瘤位置")) > 0, ]
contigtab_tumor_location <- table(tumor_location)
contigtab_tumor_location <- contigtab_tumor_location[,c(4, 3, 1, 2)]
write.csv(contigtab_tumor_location, file = "./result.csv", row.names = TRUE)
df <- read.csv("./result.csv")
df
```

```{r}
library(DescTools)
result1 <- chisq.test(contigtab_tumor_location, simulate.p.value = TRUE)
result2 <- fisher.test(contigtab_tumor_location, simulate.p.value=TRUE)
result3 <- GTest(contigtab_tumor_location)
result1
result2
result3
```

### Fourth-ventricle infiltration

```{r}
inflitration <- filtered_data[c("Fourth.ventricle.Infiltration", "Molecular.Subtypes")]
inflitration <- inflitration[nchar(as.character(inflitration$"Fourth.ventricle.Infiltration")) > 0, ]
inflitration$Fourth.ventricle.Infiltration <- ifelse(inflitration$Fourth.ventricle.Infiltration == '1. Y', 'Y', inflitration$Fourth.ventricle.Infiltration)
inflitration$Fourth.ventricle.Infiltration <- ifelse(inflitration$Fourth.ventricle.Infiltration == '2. N', 'N', inflitration$Fourth.ventricle.Infiltration)

contigtab_inflitration <- table(inflitration)
contigtab_inflitration <- contigtab_inflitration[,c(4, 3, 1, 2)]

write.csv(contigtab_inflitration, file = "./result.csv", row.names = TRUE)
df <- read.csv("./result.csv")

result1 <- chisq.test(contigtab_inflitration, simulate.p.value = TRUE)
#result2 <- fisher.test(contigtab_inflitration) 
result3 <- GTest(contigtab_inflitration)
contigtab_inflitration
result1
result2
result3
df
contigtab_inflitration
```

### Tumor Margin

```{r}
Tumor_Margin <- filtered_data[c("肿瘤边界..Tumor.Margin.", "Molecular.Subtypes")]
Tumor_Margin <- Tumor_Margin[nchar(as.character(Tumor_Margin$"肿瘤边界..Tumor.Margin.")) > 0, ]
Tumor_Margin
```

```{r}
contigtab_tumor_margin <- table(Tumor_Margin)
contigtab_tumor_margin <- contigtab_tumor_margin[, c(4, 3, 1, 2)]

write.csv(contigtab_tumor_margin, file = "./result.csv", row.names = TRUE)
df <- read.csv("./result.csv")

result1 <- fisher.test(contigtab_tumor_margin)
result2 <- chisq.test(contigtab_tumor_margin)
contigtab_tumor_margin
result1
result2
df
```

### Peritumoral edema

```{r}
peritumoral_edema <- filtered_data[c("水肿", "Molecular.Subtypes")]
peritumoral_edema <- peritumoral_edema[nchar(as.character(peritumoral_edema$"水肿")) > 0, ]
contigtab_peritumoral_edema <- table(peritumoral_edema)
contigtab_peritumoral_edema <- contigtab_peritumoral_edema[, c(4, 3, 1, 2)]

write.csv(contigtab_peritumoral_edema, file = "./result.csv", row.names = TRUE)
df <- read.csv("./result.csv")

result1 <- chisq.test(contigtab_peritumoral_edema)
result2 <- fisher.test(contigtab_peritumoral_edema)
result3 <- GTest(contigtab_peritumoral_edema, correct = "williams")
contigtab_peritumoral_edema
result1
result2
result3
df
```

### Cystic change/necrosis

```{r}
cystic <- filtered_data[c("囊肿.坏死.cyst.cavitation.change", "Molecular.Subtypes")]
cystic <- cystic[nchar(as.character(cystic$"囊肿.坏死.cyst.cavitation.change")) > 0, ]
contigtab_cystic <- table(cystic)
contigtab_cystic <- contigtab_cystic[,c(4, 3, 1, 2)]

write.csv(contigtab_cystic, file = "./result.csv", row.names = TRUE)
df <- read.csv("./result.csv")


result1 <- chisq.test(contigtab_cystic)
result2 <- fisher.test(contigtab_cystic)
result3 <- GTest(contigtab_cystic, correct = "williams")
contigtab_cystic
result1
result2
result3
df
```

### Hydrocephalus_before_Surgery

```{r}
hydrocephalus <- filtered_data[c("脑积水.手术前.", "Molecular.Subtypes")]
hydrocephalus <- hydrocephalus[nchar(as.character(hydrocephalus$"脑积水.手术前.")) > 0, ]

hydrocephalus$脑积水.手术前. <- ifelse(hydrocephalus$脑积水.手术前. == '1. Y', 'Y', hydrocephalus$脑积水.手术前.)
hydrocephalus$脑积水.手术前. <- ifelse(hydrocephalus$脑积水.手术前. == '2. N', 'N', hydrocephalus$脑积水.手术前.)

contigtab_hydrocephalus <- table(hydrocephalus)
contigtab_hydrocephalus <- contigtab_hydrocephalus[,c(4, 3, 1, 2)]

write.csv(contigtab_hydrocephalus, file = "./result.csv", row.names = TRUE)
df <- read.csv("./result.csv")

result1 <- chisq.test(contigtab_hydrocephalus)
#result2 <- fisher.test(contigtab_hydrocephalus)
result3 <- GTest(contigtab_hydrocephalus, correct = "williams")
contigtab_hydrocephalus
#proportion
result1
result2
result3
df
```

## M2 dissemination

```{r}
M2_metas <- filtered_data[c("脑部.M2.转移", "Molecular.Subtypes")]
M2_metas <- M2_metas[nchar(as.character(M2_metas$"脑部.M2.转移"))>0 ,]
M2_metas$脑部.M2.转移 <- ifelse(M2_metas$脑部.M2.转移 == '1. Y', 'Y', M2_metas$脑部.M2.转移)
M2_metas$脑部.M2.转移 <- ifelse(M2_metas$脑部.M2.转移 == '2. N', 'N', M2_metas$脑部.M2.转移)
M2_metas <- M2_metas[M2_metas$脑部.M2.转移 %in% c("N", "Y" ), ]
contigtab <- table(M2_metas)
contigtab <- contigtab[,c(4, 3, 1, 2)]

write.csv(contigtab, file = "./result.csv", row.names = TRUE)
df <- read.csv("./result.csv")

result1 <- chisq.test(contigtab)
result2 <- fisher.test(contigtab)
result3 <- GTest(contigtab, correct = "williams")
contigtab
#proportion
result1
result2
result3
df
```

# Imaging features-SHH TP53

## Data selected by genetic mutations

```{r}
selected_data <- subset(data, `Genetic.Mutations` %in% c("TP53+", "TP53-"))
selected_data <- subset(selected_data, `Molecular.Subtypes` %in% c("SHH"))
selected_data
```

### Tumor location with six classes

```{r}
tumor_location <- selected_data[c("肿瘤位置", "Genetic.Mutations")]
tumor_location <- tumor_location[nchar(as.character(tumor_location$"肿瘤位置")) > 0, ]
contigtab_tumor_location <- table(tumor_location)
result1 <- chisq.test(contigtab_tumor_location)
result1_1 <- chisq.test(contigtab_tumor_location, simulate.p.value = TRUE)
result2 <- fisher.test(contigtab_tumor_location)
write.csv(contigtab_tumor_location, file = "my_contingency_table.csv", row.names = FALSE)
contigtab_tumor_location
result1
result2
result1_1
```

The result of the chi-square test is probably incorrect, so we can try another test: G-test of independence:

```{r}
#first to install the package
install.packages("DescTools")
```

```{r}
# then import the library and calculate

library(DescTools)

result3 <- GTest(contigtab_tumor_location, correct = "williams")
result3
```

### Fourth-ventricle infiltration

```{r}
inflitration <- selected_data[c("Fourth.ventricle.Infiltration", "Genetic.Mutations")]
inflitration <- inflitration[nchar(as.character(inflitration$"Fourth.ventricle.Infiltration")) > 0, ]
contigtab_inflitration <- table(inflitration)
contigtab_inflitration <- contigtab_inflitration[,c(2,1)]
print(contigtab_inflitration)
result1 <- chisq.test(contigtab_inflitration)
result2 <- fisher.test(contigtab_inflitration) 
result3 <- GTest(contigtab_inflitration, correct = "williams")
result1
result2
result3
write.csv(contigtab_inflitration, file = "my_contingency_table.csv", row.names = FALSE)
```

### Tumor Margin

```{r}
Tumor_Margin <- selected_data[c("肿瘤边界..Tumor.Margin.", "Genetic.Mutations")]
Tumor_Margin <- Tumor_Margin[nchar(as.character(Tumor_Margin$"肿瘤边界..Tumor.Margin.")) > 0, ]
contigtab_tumor_margin <- table(Tumor_Margin)
contigtab_tumor_margin <- contigtab_tumor_margin[,c(2,1)]
result1 <- chisq.test(contigtab_tumor_margin)
result2 <- fisher.test(contigtab_tumor_margin)
result3 <- GTest(contigtab_tumor_margin, correct = "williams")
contigtab_tumor_margin
result1
result2
result3
write.csv(contigtab_tumor_margin, file = "my_contingency_table.csv", row.names = FALSE)
```

### Peritumoral edema

```{r}
peritumoral_edema <- selected_data[c("水肿", "Genetic.Mutations")]
peritumoral_edema <- peritumoral_edema[nchar(as.character(peritumoral_edema$"水肿")) > 0, ]
contigtab_peritumoral_edema <- table(peritumoral_edema)
contigtab_peritumoral_edema <- contigtab_peritumoral_edema[,c(2,1)]
result1 <- chisq.test(contigtab_peritumoral_edema)
result2 <- fisher.test(contigtab_peritumoral_edema)
result3 <- GTest(contigtab_peritumoral_edema)
contigtab_peritumoral_edema
result1
result2
result3
write.csv(contigtab_peritumoral_edema, file = "my_contingency_table.csv", row.names = FALSE)
```

### Cystic change/necrosis

```{r}
cystic <- selected_data[c("囊肿.坏死.cyst.cavitation.change", "Genetic.Mutations")]
cystic <- cystic[nchar(as.character(cystic$"囊肿.坏死.cyst.cavitation.change")) > 0, ]
contigtab_cystic <- table(cystic)

result1 <- chisq.test(contigtab_cystic)
result2 <- fisher.test(contigtab_cystic)
result3 <- GTest(contigtab_cystic)
contigtab_cystic
result1
result2
result3
```

### Hydrocephalus_before_Surgery

```{r}
hydrocephalus <- selected_data[c("脑积水.手术前.", "Genetic.Mutations")]
hydrocephalus <- hydrocephalus[nchar(as.character(hydrocephalus$"脑积水.手术前.")) > 0, ]
contigtab_hydrocephalus <- table(hydrocephalus)
result1 <- chisq.test(contigtab_hydrocephalus)
result2 <- fisher.test(contigtab_hydrocephalus)
result3 <- GTest(contigtab_hydrocephalus)
contigtab_hydrocephalus
result1
result2
result3
```

## M2 dissemination

```{r}
M2_metas <- selected_data[c("脑部.M2.转移", "Genetic.Mutations")]
M2_metas <- M2_metas[nchar(as.character(M2_metas$"脑部.M2.转移"))>0 ,]
M2_metas$脑部.M2.转移 <- ifelse(M2_metas$脑部.M2.转移 == '1. Y', 'Y', M2_metas$脑部.M2.转移)
M2_metas$脑部.M2.转移 <- ifelse(M2_metas$脑部.M2.转移 == '2. N', 'N', M2_metas$脑部.M2.转移)
M2_metas <- M2_metas[M2_metas$脑部.M2.转移 %in% c("N", "Y" ), ]
contigtab <- table(M2_metas)
#contigtab <- contigtab[,c(1, 2)]
result1 <- chisq.test(contigtab)
result2 <- fisher.test(contigtab)
result3 <- GTest(contigtab, correct = "williams")
contigtab
#proportion
result1
result2
result3
```
